### 2013-10-08 chi2014/qualitative.tex
updates

We identified X \emph{orthogonal} strategy categories - each category of strategies can be employed by a participant with or without any of the other categories.
The first, \emph{problem scoping}, is a process in which a participant chooses a limited implication or component of the problem and provides multiple specific solutions.
The second category expands on the \emph{riffing} phenomenon introduced earlier, identifying X different types of riffing exployed.
Finally, \emph{time-saving} strategies increase the rate of idea generation.
%Finally, the \emph{humour} strategy emphasizes generating ideas that are amusing rather than practical.

@@

Another phenomenon is \emph{language repitition}. Some participants seem to use common sentence structure as queues when generating ideas. For example:

@@

\subsubsection{Time-saving}

Two time-saving strategies were also identified. The first, perhaps overly obvious strategy, is \emph{brevity}. This is simply the act of keeping responses as concise as possible, presumably in the interest of finishing quickly. The second time-saving strategy was \emph{cop-outs}. Cop-outs occur when participants choose to resort to vague or iunrelated responses that do not actually provide any solution to the problem. For example, one participant's response to the MP3 player problem was to "Remove glass screen to make something". Cop-out responses may provide one or more steps towards a solution, but no solution.

Time-saving strategies tend to negatively impact the quality of responses. While there are succinct, creative responses, many brief responses are often a sign that the ideas within the run are "low-hanging fruit". Cop-out ideas are poor quality by definition.

\subsubsection{Humour}

Some participants used \emph{humour} as a method of generating ideas. For example, one response given was "glue it to the side walk and let the fun ensue". While ideas generated under this strategy are impractical individually, this strategy is most often employed by participants who otherwise take the idea generation task seriously and perform successfully.

>>>>

We identified X \emph{orthogonal} strategy categories - each category of strategies can be employed by a participant with or without any of the other categories.
The first, \emph{problem scoping}, is a process in which a participant chooses a limited implication or component of the problem and provides multiple specific solutions.
The second category expands on the \emph{riffing} phenomenon introduced earlier, identifying X different types of riffing exployed.
Finally, \emph{language use} strategies... TODO
%Finally, the \emph{humour} strategy emphasizes generating ideas that are amusing rather than practical.

@@

\subsubsection{Language use}

Participants varied in the language they used to express their ideas. Three strategies were observed: language repitition, brevity, and ambiguity.

Some participants re-use sentence structure or phrasings accross multiple responses. We call this strategy \emph{language repitition}. For example:

@@

\emph{Brevity} is the simple strategy of producing short responses. Answers under this strategy are not neccessarily less specific than longer answers. For example "textbook audio reader" is a concise description of a very specific use for an MP3 player.

\subsubsection{Partial solutions}

Under this category of strategies, responses provide some elements of a solution to the problem, but further idea generation is required to implement the solution. Some responses provide a reduced scope, but do not explore within that scope. Others would provide a goal for a solution to obtain but not provide a plan for achieving that goal. Finally, some responses passed the problem to a third party.

Above, we described the problem scoping strategy. Some participants performed \emph{problem scoping without solution}, a variant of this strategy in which problem scoping is the only component of the response.
For example, one participant's response to the MP3 player problem was to "Remove glass screen to make something". In this case, the participant has provided a scoping of the problem (focus on the glass component) but has not actually provided a solution to the scoped problem.

When a solution is provided, it is still occasionally lacking in sufficient information to act upon. We call this strategy \emph{goal without plan}. For example, a common response to the problem was "use as art". In this case, an end goal has been established, but any implementation of the goal requires further idea generation.

Finally, responses in the \emph{pass the problem} strategy simply relocate the need for idea generation to a third party. Common responses under this strategy are "give as gift" or "donate to cancer research". These solve the original problem, but simultaneously re-open the problem under slightly changed conditions. In this case, some cancer researchers must determine what to do with broken MP3 players.
